---
title: "SQL Query Agent"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{SQL Query Agent}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## What This Agent Does

`build_sql_agent()` generates SQL from user instructions, executes it, retries
on errors, and can explain the final query.

## Step 1: Prepare a Database

```{r, eval = FALSE}
library(DBI)
library(RSQLite)

conn <- dbConnect(RSQLite::SQLite(), ":memory:")
dbWriteTable(conn, "sales", data.frame(
  region = c("North", "North", "South"),
  amount = c(120, 80, 90)
))
```

## Step 2: Build the Agent

```{r, eval = FALSE}
library(LLMAgentR)

my_llm_wrapper <- function(prompt, verbose = FALSE) "LLM response placeholder"

sql_agent <- build_sql_agent(
  model = my_llm_wrapper,
  connection = conn,
  human_validation = FALSE,
  bypass_recommended_steps = FALSE,
  bypass_explain_code = FALSE,
  verbose = FALSE
)
```

## Step 3: Run the Workflow

```{r, eval = FALSE}
initial_state <- list(
  user_instructions = "Return total sales by region.",
  max_retries = 3,
  retry_count = 0
)

final_state <- sql_agent(initial_state)
str(final_state)
```

## Notes for Beginners

- Always validate generated SQL for production use.
- Keep `human_validation = TRUE` for high-stakes databases.
- Close the connection when done: `dbDisconnect(conn)`.

